Image projections along an axis

### 2006-03-02 article/Article.tex
small fixes
darcs-hash:20060302202053-2fc9d-eda897a441ddf9e03b8b30cf5607aba46fd7cb33.gz

\begin{table}[htbp]
\centering
\begin{tabular}{cc}
\hline
Filter & execution time \\
\hline
\hline
\verb$MaximumProjectionImageFilter$ & 0.0841 s \\
\verb$MinimumProjectionImageFilter$  & 0.0846 s\\
\verb$SumProjectionImageFilter$  & 0.0872 s\\
\verb$MeanProjectionImageFilter$  & 0.0828 s\\
\verb$MedianProjectionImageFilter$  & 0.164 s\\
\verb$SigmaProjectionImageFilter$  & 0.123 s\\
\verb$BinaryProjectionImageFilter$  & 0.0848 s\\
\verb$AccumulateImageFilter$, sum  & 0.465 s\\
\verb$AccumulateImageFilter$, mean  & 0.465 s\\
\hline
\end{tabular}
\caption{Execution time with a single thread.\label{perf}}
\end{table}

@@

Figure~\ref{results} show a important increase of performance while using several
threads\footnote{It also show that the execution time is not really stable
and that the mean of 50 execution time is not enough to compare the execution
time with precision. This will be discussed in another article.}.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.5]{maximum0}
\caption{MaximumProjectionImageFilter, projection along axis x.\label{maximum0}}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.5]{maximum1}
\caption{MaximumProjectionImageFilter, projection along axis y.\label{maximum1}}
\end{figure}

>>>>

\begin{table}[htbp]
\centering
\begin{tabular}{cc}
\hline
Filter & Execution time \\
\hline
\hline
\verb$MaximumProjectionImageFilter$ & 0.0841 s \\
\verb$MinimumProjectionImageFilter$  & 0.0846 s\\
\verb$SumProjectionImageFilter$  & 0.0872 s\\
\verb$MeanProjectionImageFilter$  & 0.0828 s\\
\verb$MedianProjectionImageFilter$  & 0.164 s\\
\verb$SigmaProjectionImageFilter$  & 0.123 s\\
\verb$BinaryProjectionImageFilter$  & 0.0848 s\\
\verb$AccumulateImageFilter$, sum  & 0.465 s\\
\verb$AccumulateImageFilter$, mean  & 0.465 s\\
\hline
\end{tabular}
\caption{Execution time with a single thread.\label{perf}}
\end{table}

@@

Figure~\ref{results} show an important increase of performance while using several
threads\footnote{It also show that the execution time is not really stable
and that the mean of 50 execution time is not enough to compare the execution
time with precision. This will be discussed in another article.}.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.75]{maximum2D0}
\caption{MaximumProjectionImageFilter, projection along axis x.\label{maximum0}}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.75]{maximum2D1}
\caption{MaximumProjectionImageFilter, projection along axis y.\label{maximum1}}
\end{figure}
